---
title: "Basic Plots 03 - Line/Area"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Line plot includes 8 basic types:

- line: line
- stacked line: line_stack|stacked_line
- smooth line: line_smooth|smooth_line|curve
- smooth stacked line: line_smooth_stack|line_stack_smooth|stacked_smooth_line|curve_stack|stacked_curve
- area: area
- stacked area: area_stack|stacked_area
- smooth area: area_smooth|smooth_area
- stacked smooth area: area_smooth_stack|area_stack_smooth|stacked_smooth_area

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
titanic <- data.table::melt(apply(Titanic, c(1,4), sum))
names(titanic) <- c('Class', 'Survived', 'Count')
echartr(titanic, Class, Count, Survived, type='line') %>% setLegend(pos=3) %>%
    setTheme('infographic', width=400, height=300) %>%
    setTitle('Titanic: Survival by Cabin Class','line')
```
</td>
<td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='line_stack') %>% 
    setTheme('roma', width=400, height=300) %>% setLegend(pos=3) %>%
    setTitle('Titanic: Outcome by Cabin Class','line_stack')
```
</td></tr>
<tr><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='line_smooth') %>% 
    setLegend(pos=3) %>%
    setTheme('macarons', width=400, height=300) %>%
    setTitle('Titanic: Outcome by Cabin Class','line_smooth')
```
</td><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='line_smooth_stack') %>% 
    setLegend(pos=3) %>%
    setTheme('macarons2', width=400, height=300) %>%
    setTitle('Titanic: Outcome by Cabin Class','line_smooth_stack')
```
</td></tr>
<tr><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='area') %>% setLegend(pos=3) %>%
    setTheme('sakura', width=400, height=300) %>%
    setTitle('Titanic: Survival by Cabin Class','area')
```
</td>
<td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='area_stack') %>% 
    setTheme('shine', width=400, height=300) %>% setLegend(pos=3) %>%
    setTitle('Titanic: Outcome by Cabin Class','area_stack')
```
</td></tr>
<tr><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='area_smooth') %>% 
    setLegend(pos=3) %>%
    setTheme('red', width=400, height=300) %>%
    setTitle('Titanic: Outcome by Cabin Class','area_smooth')
```
</td><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='area_smooth_stack') %>% 
    setLegend(pos=3) %>%
    setTheme('mint', width=400, height=300) %>%
    setTitle('Titanic: Outcome by Cabin Class','area_smooth_stack')
```
</td></tr>
</table>

The keys are:

- character `x` and numeric `y`
- each combination level of `x` (and `series`) can only have one `y` data point
- Tiled and stacked bar/column charts can shift from one to another by clicking type shift buttons in the toolbox widget.
- Line/area can shift to bar charts easily using buttons in toolbox widget.

# Function Call

```r
echartr(data, x, y, <series>, <z>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Other type will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| series | data series variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  z     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'line', 'line_stack', 'stacked_line', 'line_smooth', 'smooth_line', 'curve', 'line_smooth_stack', 'line_stack_smooth', 'stacked_smooth_line', 'curve_stack', 'stacked_curve','area', 'area_stack', 'stacked_area', 'area_smooth', 'smooth_area', 'area_smooth_stack', 'area_stack_smooth', 'stacked_smooth_area' |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Let's look into `airquality` dataset embeded in the package `datasets`. The structure of the data.frame is as below:

```{r}
aq <- airquality
aq$Date <- as.Date(paste('1973', aq$Month, aq$Day, sep='-'))
aq$Day <- as.character(aq$Day)
aq$Month <- factor(aq$Month, labels=c("May", "Jun", "Jul", "Aug", "Sep"))
head(aq)
```

## Line Chart

### Singular Series

`type` is set 'line'.

```{r}
echartr(aq, Date, Temp, type='line') %>%
    setTitle('NY Temperature May - Sep 1973')
```

### Multiple Series

```{r}
echartr(aq, Day, Temp, Month, type='line') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

### Line Chart with Timeline

```{r}
echartr(aq, Day, Temp, z=Month, type='line') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Stacked Line Chart

Set `type` 'line_stack' or 'stacked_line'.

```{r}
echartr(aq, Day, Temp, Month, type='line_stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Smooth Line Chart

Set `type` 'curve', 'line_smooth' or 'smooth_line'.

```{r}
echartr(aq, Day, Temp, Month, type='curve') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Stacked Smooth Line Chart

Set `type` 'line_smooth_stack', 'line_stack_smooth', 'stacked_smooth_line', 'curve_stack' or 'stacked_curve'.

```{r}
echartr(aq, Day, Temp, Month, type='curve_stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Area Chart

Area chart is exactly the same with line chart except that it has `areaStyle` feature specialized.

Set `type` 'area'.

```{r}
echartr(aq, Date, Temp, type='area') %>%
    setTitle('NY Temperature May - Sep 1973') %>% 
    setSymbols('emptycircle')
```

## Stacked Area Chart

Set `type` 'area_stack' or 'stacked_area'.

```{r}
echartr(aq, Day, Temp, Month, type='area_stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Smooth Area Chart

Set `type` 'area_smooth' or 'smooth_area'.

```{r}
echartr(aq, Date, Temp, type='area_smooth') %>%
    setTitle('NY Temperature May - Sep 1973') %>% 
    setSymbols('emptycircle')
```

## Stacked Smooth Area Chart

Set `type` 'area_smooth_stack', 'area_stack_smooth' or 'stacked_smooth_area'.

```{r}
echartr(aq, Day, Temp, Month, type='area_smooth_stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

