---
title: "Basic Plots 01 - Scatterplot"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Scatter plot includes:
- simple scatter/point
- bubble

For scatter plots, `x` and `y` must both be numeric.

# Simple Scatter Plot

## Single Series

```{r}
echartr(iris, Sepal.Width, Petal.Width)
```

It is equivalent to

```r
echartr(iris, x=Sepal.Width, y=Petal.Width, type='scatter')
echartr(iris, Sepal.Width, Petal.Width, type='point')
echartr(iris, Sepal.Width, Petal.Width, type='bubble')
```

## Multiple Series

```{r}
echartr(iris, Sepal.Width, Petal.Width, Species)
```

# Bubble Chart

The key is to pass `weight` variable. If `weight` is accepted, no matter the `type` variable is 'scatter', 'point' or 'bubble', a bubble chart will display.

```{r}
echartr(iris, Sepal.Width, Petal.Width, weight=Petal.Length)
```

# Scatter Plot with Timeline

Timeline calls for numeric or time variable. When a character variable is passed in, `echarts` coerces it to numeric.

```{r}
echartr(iris, Sepal.Width, Petal.Width, z=Species)
```

# Aesthetics

Of course you can apply `setTheme` or `setSymbols` to modify the charts

```{r}
g <- echartr(iris, Sepal.Width, Petal.Width, Species)
```

- Apply 'vintage' theme and set the width 500 px, height 350 px.

```{r}
g %>% setTheme('vintage', width=500, height=350)
```


- Apply non-standard symbols c('star6', 'emptyCircle', 'heart') to `symbolList`.

```{r}
rm(g)
g = echartr(iris, Sepal.Width, Petal.Width, Species) %>% 
  setTheme('macarons') %>% setSymbols(c('star6', 'emptyCircle', 'heart')) 
g
```


- Move `legend` to 12 o'clock position, `toolbox` to 9 o'clock position. 
- Set `title` = 'Iris Flowers' at the 6 o'clock position.

```{r}
rm(g)
g = echartr(iris, Sepal.Width, Petal.Width, Species) %>% 
  setLegend(pos=12) %>% setToolbox(pos=9) %>% 
  setTitle("Iris Flowers", pos=6) %>% setTheme('helianthus')
g
```

You can refer to related functions to play around on your own.
