---
title: "recharts: An R Interface to ECharts"
output: 
  html_document: 
    toc: yes
---

---

<div class="alert alert-warning">

<strong>Note:</strong> This package is still under active development. It is based on the last release of Echarts2 (v2.2.7). The documentation here always reflects the latest development version of **recharts** on [Github](https://github.com/madlogos/recharts). To install the package:

```r
if (!require(devtools)) library(devtools)
install_github("madlogos/recharts")
```

</div>

# Knowledge Map of the Guidance

1. Base Plots
    1. Cartesian Coordinate System
        1. [Scatter/Bubble Plot](Basic_Plots_01_Scatterplot.html)
        1. [Bar/Column Chart](Basic_Plots_02_Bar.html)
        1. [Line/Area Chart](Basic_Plots_03_Line.html)
        1. [Candlestick Chart](Basic_Plots_04_K.html)
    1. Polar Coordinate System
        1. [Pie/Ring/Rose Chart](Basic_Plots_11_Pie.html)
        1. [Funnel/Pyramid Chart](Basic_Plots_12_Funnel.html)
        1. [Radar Chart](Basic_Plots_13_Radar.html)
    1. Other Plots
        1. [Map](Basic_Plots_21_Map.html)
        1. [Force Chart](Basic_Plots_22_Force.html)
        1. [Chord Chart](Basic_Plots_23_Chord.html)
        1. [Tree Chart](Basic_Plots_24_Tree.html)
        1. [Treemap](Basic_Plots_25_Treemap.html)
        1. [Word Cloud](Basic_Plots_26_Wordcloud.html)
        1. [Venn Chart](Basic_Plots_27_Venn.html)
        1. [River Event Chart](Basic_Plots_28_RiverEvent.html)
        1. [Gauge Chart](Basic_Plots_29_Gauge.html)
    
1. Mixed Plots

1. Axis/Widget Configuration
    - Axis/Grid
    1. [`setAxis`](Widget_01_Axis.html)
    1. [`setPolar`](Widget_02_Polar.html)
    1. [`setGrid`](Widget_03_Grid.html)
    - Widgets
    1. [`setTitle`](Widget_11_Title.html)
    1. [`setLegend`](Widget_12_Legend.html)
    1. [`setTimeline`](Widget_13_Timeline.html)
    1. [`setToolbox`](Widget_14_Toolbox.html)
    1. [`setDataRange`](Widget_15_DataRange.html)
    1. [`setDataZoom`](Widget_16_DataZoom.html)
    1. [`setRoam`](Widget_17_RoamController.html)

1. Aesthetic Configuration
    1. [`setTooltip`](Widget_21_Tooltip.html)
    1. [`setSymbols`](Widget_22_SymbolList.html)
    1. [`setTheme`](Widget_23_Theme.html)
    1. [`relocWidget`](Widget_11_Relocation.html)
    
1. Customization

# Hello World

The R package **recharts** provides an interface to the JavaScript library [ECharts2](http://echarts.baidu.com/echarts2) for data visualization. The goal of this package is to make it easy to create charts with only a few lines of R code. R users should be able to get started with ECharts without having to know HTML or JavaScript, although advanced users will benefit from their knowledge of JavaScript. Here is an example of a scatterplot that shows the basic syntax of this package:

```{r}
library(recharts)
echartr(iris, ~Sepal.Length, ~Sepal.Width, series = ~Species)
```

The **recharts** package was built on top of [**htmlwidgets**](http://htmlwidgets.org), which can save us a lot of time on managing JavaScript dependencies and dealing with different types of output documents such as R Markdown and Shiny. You just create a chart, and we will take care of the rest of things when the chart is renderd in R Markdown, Shiny, or the R console / RStudio.

The main function in this package is the `echartr()` function (an S3 generic function), and we want to make it smart enough to deal with different types of R data automatically. For example, when a data frame is passed to `echart()`, and the `x`/`y` variables are numeric, it should automatically figure out that you probably need a scatterplot, and the axes will be automatically generated. Of course, you can also override the automatic guess.

# Quick Start

Follow the steps below to make a plot yourself.

## Data
Always start from data itself. Let's use `mtcars`.

```{r}
head(mtcars)
```

We want to know the relationship between `wt` (weight) and `mpg` (miles per gallon), a scatterplot is a good fit. It requires x and y variables of numeric.

## Core Plot

Use `echartr` to build the basic chart.

```{r}
echartr(mtcars, wt, mpg)
```

The grammar of `echartr` is 

```{r, echo=FALSE}
str(args(echartr))
```

|   **Arg**        |               **Meaning**               |
|:----------|:--------------------------------------------------------------|
| **data** | source data in form of data.frame |
| **x** | independent variable(s). One or more columns of `data`. Could be time, numeric or characters. |
| **y** | dependent variable(s). One or more columns of `data`. Always numeric. |
| **series** | series variable. A column of `data` which is treated as factors. |
| **weight** | weight variable used in bubble chart. |
| **z** | time variable. If `z` is assigned, a timeline widget will display. |
| **lat** | latitude variable for map. |
| **lng** | longitude variable for map. |
| **type** | chart type. Default 'auto'. |

`echartr` now support the following types (the regex patterns in 'name' column, case insensitive):
```{r}
knitr::kable(recharts:::validChartTypes[,2:7])
```

You assign `data` and `x`, `y`, then `echartr` automatically processes the data using `recharts:::series_scatter` function.

If `series` is assigned, a series-specfic scatterplot is shown. If `weight` is assigned, a bubble chart is displayed.

```{r}
echartr(mtcars, wt, mpg, factor(am, labels=c('Automatic', 'Manual')))
echartr(mtcars, wt, mpg, am, weight=gear)
```

The input param list could be

- symbols: wt, mpg or even as complicated as `factor(am, labels=c('Automatic', 'Mannual'))`
- characters: 'wt', 'mpg'
- formulas: ~wt, ~mpg

## Modify the Plot

You can save the plot as an object and keep modifying the plot using `%>%`.

### Title

```{r}
g = echartr(mtcars, wt, mpg, factor(am, labels=c('Automatic', 'Mannual')))
g %>% setTitle('wt vs mpg', 'Motor Trend', textStyle=list(color='red'))
```

### Legend

```{r}
g %>% setLegend(selected='Automatic', textStyle=list(color='green'))
```

### Toolbox

```{r}
g %>% setToolbox(lang='en', pos=2)
```

### DataZoom

```{r}
g %>% setDataZoom()
```

### Axis

```{r}
g %>% setXAxis(min=0) %>% setYAxis(min=0)
```

## Fortify the Chart

### Theme

```{r}
g %>% setTheme('shine', calculable=TRUE)
```

### Symbols

```{r}
g %>% setSymbols('heart')
```

## Altogether

You can combine all the steps using a pipe chain. If you are familiar with JS, you can embed JS fragments using `JS()` for better effects.

```{r}
g %>% setTitle('wt vs mpg', 'Motor Trend', textStyle=list(color='red')) %>%
    setLegend(selected='Automatic', textStyle=list(color='green')) %>%
    setToolbox(lang='en', pos=2) %>% setDataZoom() %>% 
    setTheme('dark', calculable=TRUE) %>% setSymbols('heart')
```

# Low-level API

Given that ECharts supports so many types of charts, it may take a while for us to make `echartr()` really smart. With that in mind, we also provided a really low-level S3 method defined for lists. Since the main usage of ECharts is that you pass a JavaScript object to the method `.setOption()`, and we can construct such an object using a list in R. This low-level `echart.list()` method makes it possible for you to create arbitrary charts. Here is a simple example of a Chord diagram taken from http://echarts.baidu.com/doc/example/chord1.html:

```{r}
chordEx1 = list(
  title = list(
    text = '测试数据',
    subtext = 'From d3.js',
    x = 'right',
    y = 'bottom'
  ),
  tooltip = list(
    trigger = 'item',
    formatter = JS('function(params) {
      if (params.indicator2) { // is edge
        return params.value.weight;
      } else {// is node
        return params.name
      }
    }')
  ),
  toolbox = list(
    show = TRUE,
    feature = list(
      restore = list(show = TRUE),
      magicType = list(show = TRUE, type = c('force', 'chord')),
      saveAsImage = list(show = TRUE)
    )
  ),
  legend = list(
    x = 'left',
    data = c('group1', 'group2', 'group3', 'group4')
  ),
  series = list(
    list(
      type = 'chord',
      sort = 'ascending',
      sortSub = 'descending',
      showScale = TRUE,
      showScaleText = TRUE,
      data = list(
        list(name = 'group1'),
        list(name = 'group2'),
        list(name = 'group3'),
        list(name = 'group4')
      ),
      itemStyle = list(
        normal = list(
          label = list(show = FALSE)
        )
      ),
      matrix = rbind(
        c(11975,  5871, 8916, 2868),
        c( 1951, 10048, 2060, 6171),
        c( 8010, 16145, 8090, 8045),
        c( 1013,   990,  940, 6907)
      )
    )
  )
)

echart(chordEx1)
```

Apparently, all we did was to translate the JavaScript object in the [original example](http://echarts.baidu.com/doc/example/chord1.html) into R. Note we translated the function `tooltip.fomatter` using the `JS()` function in **htmlwidgets**. All other objects can be mapped naturally to R.

# Finale

Normally we do not want R users to specify a long list of options like that. As R users, you are more familiar with (and often work with) data structures like data frames, matrices, tables, and so on. Ideally we hope you can just pass a familiar data object, and we configure ECharts automatically for you whenever possible. We are still _far away_ from our goal at this moment, but we will be happy to know your feedback, and you are welcome to contribute code through [Github pull requests](https://github.com/yihui/recharts).
